PMV: Which formulation should you use the ISO 7730:2005 or ASHRAE 55:2020?

### 2023-09-01 Manuscript/src/sections/results.tex
Updates from Overleaf

The \ac{pmv-ce} was specifically developed to more accurately estimate latent and sensible heat losses from the skin to the environment when air movement is used.
However, our results show that the \ac{pmv-ce} is less accurate than the \ac{pmv} in predicting people who were `slightly warm'.
Both models had an accuracy lower than \qty{1}{\percent} when predicting either `warm', `hot', or `cold'.
This value is significantly lower and worse than random guessing, this is very concerning because this means that the models are actively misleading the users.
The low prediction accuracy of both model formulations, coupled with the lack of data in the extremes of the applicability limits of the models, may suggest that the models' applicability limits should be revisited.
Based on the results, we suggest that the Standards applicability limits could be reduced to the following range \qty{18}{\celsius}~$\leq$~\ac{tdb}~$\leq$~\qty{30}{\celsius} and \qty{10}{\celsius}~$\leq$~\ac{tr}~$\leq$~\qty{30}{\celsius} (instead of \qty{10}{\celsius}~$\leq$~\ac{tdb}~$\leq$~\qty{30}{\celsius} and \qty{10}{\celsius}~$\leq$~\ac{tr}~$\leq$~\qty{40}{\celsius}),  until more data are collected.

>>>>

The \ac{pmv-ce} was specifically developed to more accurately estimate latent and sensible heat losses from the skin to the environment when air movement is used~\cite{arens_moving_2009}.
However, our results show that the \ac{pmv-ce} is less accurate than the \ac{pmv} in predicting people who were `slightly warm'.
Both models had an accuracy lower than \qty{1}{\percent} when predicting either `warm', `hot', or `cold'.
This value is significantly lower and worse than random guessing, this is very concerning because this means that the models are actively misleading the users.
The low prediction accuracy of both model formulations, coupled with the lack of data in the extremes of the applicability limits of the models, may suggest that the models' applicability limits should be revisited.
Based on the results, we suggest that the Standards applicability limits could be reduced to the following range \qty{18}{\celsius}~$\leq$~\ac{tdb}~$\leq$~\qty{30}{\celsius} and \qty{10}{\celsius}~$\leq$~\ac{tr}~$\leq$~\qty{30}{\celsius} (instead of \qty{10}{\celsius}~$\leq$~\ac{tdb}~$\leq$~\qty{30}{\celsius} and \qty{10}{\celsius}~$\leq$~\ac{tr}~$\leq$~\qty{40}{\celsius}),  until more data are collected.
